\documentclass[10pt]{article}

\usepackage{calc}
  \usepackage{verbatim}
  \usepackage{eurosym}

\reversemarginpar
\usepackage[paper=letterpaper,
            marginparwidth=1.2in,     % Length of section titles
            marginparsep=.05in,       % Space between titles and text
            margin=1in,               % 1 inch margins
            includemp]{geometry}

\setlength{\parindent}{0in}
\usepackage{paralist}
\usepackage{fancyhdr,lastpage}
\pagestyle{fancy}
\fancyhf{}\renewcommand{\headrulewidth}{0pt}
\fancyfootoffset{\marginparsep+\marginparwidth}
\newlength{\footpageshift}
\setlength{\footpageshift}
          {0.5\textwidth+0.5\marginparsep+0.5\marginparwidth-2in}
\lfoot{\hspace{\footpageshift}%w
       \parbox{4in}{\, \hfill %
                   % \arabic{page} of \protect\pageref*{LastPage} % +LP	         
                               \arabic{page}                               % -LP
                    \hfill \,}}

% Finally, give us PDF bookmarks
\usepackage{color,hyperref}
\usepackage[latin1]{inputenc} 

\definecolor{darkblue}{rgb}{0.0,0.0,0.3}
\hypersetup{colorlinks,breaklinks,
            linkcolor=darkblue,urlcolor=darkblue,
            anchorcolor=darkblue,citecolor=darkblue}

\newcommand{\makeheading}[1]%
        {\hspace*{-\marginparsep minus \marginparwidth}%
         \begin{minipage}[t]{\textwidth+\marginparwidth+\marginparsep}%
                {\large \bfseries #1}\\[-0.15\baselineskip]%
                 \rule{\columnwidth}{1pt}%
         \end{minipage}}

\renewcommand{\section}[2]%
        {\pagebreak[2]\vspace{1.3\baselineskip}%
         \phantomsection\addcontentsline{toc}{section}{#1}%
         \hspace{0in}%
         \marginpar{
         \raggedright \scshape #1}#2}

\newenvironment{outerlist}[1][\enskip\textbullet]%
        {\begin{itemize}[#1]}{\end{itemize}%
         \vspace{-.6\baselineskip}}

\newenvironment{lonelist}[1][\enskip\textbullet]%
        {\vspace{-\baselineskip}\begin{list}{#1}{%
        \setlength{\partopsep}{0pt}%
        \setlength{\topsep}{0pt}}}
        {\end{list}\vspace{-.6\baselineskip}}

\newenvironment{innerlist}[1][\enskip\textbullet]%
        {\begin{compactitem}[#1]}{\end{compactitem}}

\newcommand{\blankline}{\quad\pagebreak[2]}

\begin{document}
\makeheading{Carlos E. L\'{o}pez Camey}

\section{Contact Information}
%
% NOTE: Mind where the & separators and \\ breaks are in the following
%       table.
%
% ALSO: \rcollength is the width of the right column of the table 
%       (adjust it to your liking; default is 1.85in).
%
\newlength{\rcollength}\setlength{\rcollength}{1.85in}%
%
\begin{tabular}[t]{@{}p{\textwidth-\rcollength}p{\rcollength}}
St\"{o}ckenh\"{o}fe 6, 
79299, Wittnau, Germany 
& \href{http://www.kmels.net/}{http://kmels.net} \\
& \href{mailto:c.lopez@kmels.net}{c.lopez@kmels.net} \\
& \textit{Tel:} +49 0160 9671 2326 \\

\end{tabular}

\section{Birth and Citizenship} 05.12.1989, Guatemala

\section{Education}
\href{http://www.uni-freiburg.de/}{\textbf{University of Freiburg}}, 
Freiburg im Breisgau, Germany
\begin{outerlist}

\item[] B.Sc. in Computer Science (2012-2014)
\end{outerlist}

\blankline

\href{http://www.uvg.edu.gt/}{\textbf{Universidad Del Valle de Guatemala}}, 
Guatemala City, Guatemala
\begin{outerlist}

\item[] Three and a half years of B.Sc. in Computer Science (2008-2011) 
       \begin{innerlist}
       \item Interim President of the Computer Science Students Association, 2009
       \item Teaching Assistant, Algorithms and Data Structures, 2010 and 2011 
       \end{innerlist}
\end{outerlist}

\blankline

\href{http://www.suizoamericano.edu.gt/}{\textbf{Colegio Suizo Americano}}, 
Guatemala City, Guatemala
\begin{outerlist}
\item[] Programming oriented High School
        (2006-2007)
\end{outerlist}

\blankline

\section{Scholarships}
\href{http://www.uu.nl/}{\textbf{Universiteit Utrecht}}, Utrecht, Netherlands 

\begin{outerlist}
\item[] \href{http://www.utrechtsummerschool.nl/index.php?type=courses&code=H9}{Applied Functional Programming in Haskell} (2012)
        \hfill Full course scholarship (835 euros)
\end{outerlist}

\blankline

\href{http://www.sigplan.org/}{\textbf{ACM SIGPLAN-SIGACT}}, Rome, Italy, 2013 

\begin{outerlist}
\item[] \href{http://popl.mpi-sws.org/2013/}{40th Symposium on Principles of Programming Languages} (2013)
        \hfill Registration and travel expenses (950 US dollars)
\end{outerlist}

\blankline

\section{Work experience} 
% Digitalgeko
\href{http://proglang.informatik.uni-freiburg.de/}{\textbf{Programming Languages Group}}, University of Freiburg
\begin{outerlist}
\item[] \textit{Research Assistant}%
        \hfill \textbf{February 2013-}
        \begin{innerlist}
        \item DART Haskell, a program that detects errors in Haskell programs
        \end{innerlist}
\end{outerlist}

% Digitalgeko
\href{http://www.digitalgeko.com/}{\textbf{Digitalgeko}}, 
\begin{outerlist}
\item[] \textit{Web Developer}%
        \hfill \textbf{Aug 2010-Jan 2011}
        \begin{innerlist}
        \item Participated in the development of two systems for the Goverment of Timor-Leste in a team of 4 persons. Java technologies were used (Spring Framework, Hibernate, Stripes Framework).
        \item Implemented a website in TYPO3.
        \end{innerlist}
\end{outerlist}

\blankline

\href{http://www.tecnomaya.net/}{\textbf{Tecnomaya S.A.}}, 
Guatemala City, Guatemala

\begin{outerlist}
\item[] \textit{System Administrator/Mantainer.}%
        \hfill \textbf{Jan 2008-Apr 2009}
        \begin{innerlist}
        \item Developed the apportionment system control in MS Access.
        \item The intranet system, based on SugarCRM and the Xoops Platform.
        \end{innerlist}
\end{outerlist}

\blankline

{\textbf{Elex de Guatemala S.A.}}
\begin{outerlist}
\item[] \textit{Freelance, } \hfill \textbf{Jan 2011-May 2011}
        \begin{innerlist}
        \item Redesigned database to implement an admin interface in \href{http://elexsa.com}{elexsa.com}
        \item Implemented mobile website version in \href{http://elexsa.com/movil}{elexsa.com/movil}
        \end{innerlist}
\end{outerlist}

\blankline

\section{Open source project contributions}

\textbf{XMonad}, worked on XMonad.Prompt and created the module XMonad.Actions.Launcher

\blankline

\section{Technical} \textbf{Programming languages:} Java (2 years of experience), Scala (1 year), Haskell (6 months). 

\blankline

\textbf{Less often or previously used:} Javascript, PHP, Python, Emacs and Common Lisp, C, Assembly 8086.

\blankline

\textbf{Versioning Control Systems:} SVN, Mercurial, Git, darcs.

\blankline

\textbf{Operating Systems:} Mac OS X, Windows XP/Vista, Linux Ubuntu.

\blankline

\textbf{Tools and Libraries:} Play framework, \LaTeX{}, PGF (TikZ), sage, gnuplot, HTML and CSS, GTK.

\blankline

\section{Interests and Hobbies}
The art of programming, Functional Programming, program verification, Free and Open Source Software, Mathematical Logic, Music, Squash, Beer.

\blankline

\section{Current/past organization Membership}
\textbf{Universidad del Valle de Guatemala, Computer Science Students Association} (AECC), 2009-2010.

\section{Language Skills}
Spanish: Native speaker

\blankline

English: Fluent, 15+ years of continuous practice)

\blankline

German: Conversational/Fluent

\blankline

Official certificates:
\begin{outerlist}  
  \item \textbf{DSH-2}, Language Teaching Center, University of Freiburg. \hfill \textbf{2012}
  \item \textbf{TOEFL}, Advanced in writing, hearing and reading. Intermediate in speaking. \hfill \textbf{2012}
  \item \textbf{ELASH}, Colegio Suizo Americano    \hfill \textbf{2007}
  \item  \textbf{Embassy Certificate of English}, Embasy CES \hfill \textbf{2007}
\end{outerlist}

\section{Miscellaneous Courses}
\textbf{Applescript with Sal Soghoian}, MacWorld Expo 2009, \textit{San Francisco, CA.} \hfill \textbf{Jan 2009}

\blankline

\textbf{Embassy Certificate of English}, Embasy CES,
\textit{Hastings, UK}  \hfill \textbf{Nov 2007}

\blankline

\textbf{Presentaciones Juveniles, Dale Carnegie Training}, Dale Carnegie \& Associates, Inc., \textit{Guatemala City, Guatemala}  \hfill \textbf{March 2004}

\blankline

\textbf{Dale Carnegie Course for Teenagers}, Dale Carnegie \& Associates, Inc., \textit{Guatemala City, Guatemala}  \hfill \textbf{Dec 2003}

\blankline

\section {References} Available upon request

\end{document}

%%%%%%%%%%%%%%%%%%%%%%%%%% End CV Document %%%%%%%%%%%%%%%%%%%%%%%%%%%%%
